---
output: 
  xaringan::moon_reader:
    css: [theme.css, theme-fonts.css, default, hygge, metropolis-fonts]
    seal: false
    nature:
      slideNumberFormat: "%current%"   
      highlightStyle: github
      highlightLines: true
---
class: titleSlide
<br><br><br>
.pull-left[
  ## Haplustolls
  <br><br><br>
  #### Soil Taxonomy & R Meeting - 2020/11/17
]

.right[.large[<br><br><br><br><br><br><br><br>
              Andrew G. Brown <br>
              <a href="mailto:andrew.g.brown@usda.gov"><i class="fas  fa-mail-bulk "></i>andrew.g.brown@usda.gov</a>
              <br><br>
]]

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(aqp)
library(soilDB)

if (!file.exists("haplustolls.rda")) {
  res <- soilDB:::.fetchNASIS_pedons(dfClass = "data.table")
  # check moist value and chroma, ignore dry value
  res$is_mollic_color <- hasDarkColors(res, d_value = NA)
  
  res$mtr1 <- profileApply(res, mollic.thickness.requirement, clay.attr='clay')
  darkColorInterval <- function(p) {
    mss <- getMineralSoilSurfaceDepth(p)
    p.sub <- glom(p, mss, estimateSoilDepth(p))
    return(data.frame(peiid = profile_id(p), 
                      mineral_surface = mss, 
                      darkness_depth = getSurfaceHorizonDepth(p.sub, pattern = "TRUE", hzdesgn = "is_mollic_color")))
  }
  dcdf <- profileApply(res, darkColorInterval, frameify = TRUE)
  site(res) <- dcdf
    
  diagnostic_hz(res) <- rbind(data.frame(peiid = profile_id(res), 
                                         featkind = "mollic colors", 
                                         featdept = res$mineral_surface, 
                                         featdepb = res$darkness_depth),
                        data.frame(peiid = profile_id(res), 
                                   featkind = "mollic requirement", 
                                   featdept = res$mineral_surface, 
                                   featdepb = res$mtr1))
  res$prettycolor <- with(horizons(res), sprintf("%s %s/%s", m_hue, m_value, m_chroma))
  
  save(res, file = "haplustolls.rda")
} else {
  load("haplustolls.rda")
}
# 
# plot(density(mtr1))
# # abline(v=c(10,18,20,25))
# # 
# plot(subset(res, (mtr1 - 20) == -10)[1:10,], max.depth=50)
```


---
class: bodySlide

<br>

## Strategy

 - Tabulate changes in representative (RV) Component Pedons, stratified by taxonomic Great Group
 
 - Great Group may offer a good balance of data availability v.s. partitioning of taxonomic space and spatial space
 
 - Consistent "chunks" of taxonomy (e.g. the Great Group) facilitate dispatch of potentially problematic taxa, extents, series to the relevant regional and local staff for comment/opinion
 
 - Comments and opinions from Soil Scientists would ideally be available for review by all Regional Committees (i.e. done before the proposals go live for official review)

---
class: bodySlide

<br>

## NASIS Haplustolls Representative Component Pedons (1/2)

```{r}
length(res)
table(res$darkness_depth >= res$mtr1)
table(res$darkness_depth >= 20)
```

---
class: bodySlide

<br>

## NASIS Haplustolls Representative Component Pedons (2/2)

```{r}
table(res$darkness_depth >= 25)
table(res$darkness_depth >= 30)
```

---
class: bodySlideNOBR

<br>

## Soils that do not meet the mollic requirement

First ten profiles in set.

```{r, echo=FALSE, fig.width=15}
par(mar=c(0,0,0,2))
res.sub <- subset(res, darkness_depth < mtr1)[1:10,]
plotSPC(res.sub, 
        name = "prettycolor", #color = "is_mollic_color",
        name.style = 'left-center', cex.names=1, width=0.3)
addDiagnosticBracket(res.sub, "mollic colors", offset=-0.5)
addDiagnosticBracket(res.sub, "mollic requirement", lwd=2, col="green", tick.length=0, offset=0)
```

---

class: bodySlideNOBR

<br>

## Soils that meet mollic requirement

First ten profiles in set.

```{r, echo=FALSE, fig.width=15}
par(mar=c(0,0,0,2))
res.mollic <- subset(res, darkness_depth > mtr1)[1:10,]
plotSPC(res.mollic, 
        name = "prettycolor", #color = "is_mollic_color",
        name.style = 'left-center', cex.names=1, width=0.3)
addDiagnosticBracket(res.mollic, "mollic colors", offset=-0.5)
addDiagnosticBracket(res.mollic, "mollic requirement", lwd=2, col="green", tick.length=0, offset=0)
```